Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/normalsandcurvature.tex
added II values and remove orcid

\begin{figure}
    \centering
    \begin{tabular}{c c}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                width=0.53\textwidth,
                xlabel={Gridstep},
                ylabel={RMSE error},
                x dir=reverse,
                legend pos=north east,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
            ]
                \addplot[
                    color=cyan,
                ] coordinates {
                    (0.125,0.0156736)(0.250,0.031503)(0.375,0.0384303)(0.500,0.0441086)(0.625,0.0418896)(0.750,0.0584604)(0.875,0.065503)(1.000,0.0729735)
                };
                \addplot[
                    color=red,
                ] coordinates {
                    (0.125,0.0221236)(0.250,0.0317159)(0.375,0.0542242)(0.500,0.0706101)(0.625,0.09481)(0.750,0.134544)(0.875,0.130578)(1.000,0.127371)
                };
                \addplot[
                    color=MyGreen,
                ] coordinates {
                    (0.125,0.0203851)(0.250,0.032289)(0.375,0.0353311)(0.500,0.0568694)(0.625,0.0665957)(0.750,0.106711)(0.875,0.0817172)(1.000,0.104688)
                };
                \addplot[
                    color=orange,
                ] coordinates {
                    (0.125,0.0106125)(0.250,0.0223176)(0.375,0.032738)(0.500,0.0365776)(0.625,0.0362568)(0.750,0.0181232)(0.875,0.0303189)(1.000,0.0263066)
                };
                \addplot[
                    color=black,
                    thick,
                    domain=0.1:1,
                    samples=200,
                ] {0.1*x^(0.66)} node[pos=0.2, anchor=south west] {$h^{\frac{2}{3}}$};
            \end{axis}
        \end{tikzpicture} &
        \begin{tikzpicture}
            \centering
            \begin{axis}
                [
                width=0.53\textwidth,
                xlabel={Gridstep},
                ylabel={$E_{\max}$ error},
                x dir=reverse,
                legend pos=north east,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
                ]
                \addplot[
                    color=cyan,
                ] coordinates {
                    (0.125,0.0586128)(0.250,0.0736204)(0.375,0.114564)(0.500,0.114592)(0.625,0.136021)(0.750,0.152418)(0.875,0.139939)(1.000,0.234379)
                };
                \addplot[
                    color=red,
                ] coordinates {
                    (0.125,0.0743185)(0.250,0.0810657)(0.375,0.113504)(0.500,0.145859)(0.625,0.256274)(0.750,0.266855)(0.875,0.259101)(1.000,0.274269)
                };
                \addplot[
                    color=MyGreen,
                ] coordinates {
                    (0.125,0.0670488)(0.250,0.0926269)(0.375,0.0973621)(0.500,0.137059)(0.625,0.155913)(0.750,0.290065)(0.875,0.164799)(1.000,0.317625)
                };
                \addplot[
                    color=orange,
                ] coordinates {
                    (0.125,0.0313599)(0.250,0.044124)(0.375,0.0643389)(0.500,0.0684951)(0.625,0.0853552)(0.750,0.0532733)(0.875,0.064386)(1.000,0.0873334)
                };
                \addplot[
                    color=black,
                    thick,
                    domain=0.1:1,
                    samples=200,
                ] {0.1*x^(0.5)} node[pos=0.5, anchor=north east] {$h^{\frac{1}{2}}$};
            \end{axis}
        \end{tikzpicture} \\
        \multicolumn{2}{c}{
            \begin{tikzpicture}
                \begin{axis}[
                    hide axis,
                    xmin=0, xmax=1,
                    ymin=0, ymax=1,
                    legend columns=5,
                    legend style={
                        at={(0.5,-0.2)},
                        anchor=north,
                        draw=none,
                        column sep=15pt
                    }
                ]
                    \addlegendimage{color=cyan}
                    \addlegendentry{ellipsoid}
                    \addlegendimage{color=red}
                    \addlegendentry{goursat}
                    \addlegendimage{color=MyGreen}
                    \addlegendentry{rcube}
                    \addlegendimage{color=orange}
                    \addlegendentry{sphere9}

>>>>

\begin{figure}
    \centering
    \begin{tabular}{c c}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                width=0.53\textwidth,
                xlabel={Gridstep},
                ylabel={RMSE error},
                x dir=reverse,
                legend pos=north east,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
            ]
                \addplot[
                    color=cyan,
                    mark=halfcircle
                ] coordinates {
                    (0.125,0.0156736)(0.250,0.031503)(0.375,0.0384303)(0.500,0.0441086)(0.625,0.0418896)(0.750,0.0584604)(0.875,0.065503)(1.000,0.0729735)
                };

                \addplot[
                    color=cyan,
                    mark=square
                ] coordinates {
                    (0.125,0.00669781)(0.250,0.0120283)(0.375,0.0165559)(0.500,0.0263742)(0.625,0.0270529)(0.750,0.0361097)(0.875,0.0501562)(1.000,0.04348)
                };
                \addplot[
                    color=red,
                    mark=halfcircle
                ] coordinates {
                    (0.125,0.0221236)(0.250,0.0317159)(0.375,0.0542242)(0.500,0.0706101)(0.625,0.09481)(0.750,0.134544)(0.875,0.130578)(1.000,0.127371)
                };

                \addplot[
                    color=red,
                    mark=square
                ] coordinates {
                    (0.125,0.0157673)(0.250,0.024652)(0.375,0.0343723)(0.500,0.0463823)(0.625,0.051336)(0.750,0.0763857)(0.875,0.0758734)(1.000,0.0617788)

                };
                \addplot[
                    color=MyGreen,
                    mark=halfcircle
                ] coordinates {
                    (0.125,0.0203851)(0.250,0.032289)(0.375,0.0353311)(0.500,0.0568694)(0.625,0.0665957)(0.750,0.106711)(0.875,0.0817172)(1.000,0.104688)
                };

                \addplot[
                    color=MyGreen,
                    mark=square
                ] coordinates {
                    (0.125,0.0140342)(0.250,0.0229046)(0.375,0.0304815)(0.500,0.0466803)(0.625,0.0559396)(0.750,0.0328143)(0.875,0.100956)(1.000,0.0944342)

                };
                \addplot[
                    color=orange,
                    mark=halfcircle
                ] coordinates {
                    (0.125,0.0106125)(0.250,0.0223176)(0.375,0.032738)(0.500,0.0365776)(0.625,0.0362568)(0.750,0.0181232)(0.875,0.0303189)(1.000,0.0263066)
                };

                \addplot[
                    color=orange,
                    mark=square
                ] coordinates {
                    (0.125,0.00364692)(0.250,0.00928532)(0.375,0.0168347)(0.500,0.0231946)(0.625,0.0220619)(0.750,0.0340007)(0.875,0.0533849)(1.000,0.0691569)

                };
                \addplot[
                    color=black,
                    thick,
                    domain=0.1:1,
                    samples=200,
                ] {0.1*x^(0.66)} node[pos=0.2, anchor=south west] {$h^{\frac{2}{3}}$};
            \end{axis}
        \end{tikzpicture} &
        \begin{tikzpicture}
            \centering
            \begin{axis}
                [
                width=0.53\textwidth,
                xlabel={Gridstep},
                ylabel={$E_{\max}$ error},
                x dir=reverse,
                legend pos=north east,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
                ]
                \addplot[
                    color=cyan,
                    mark=halfcircle
                ] coordinates {
                    (0.125,0.0586128)(0.250,0.0736204)(0.375,0.114564)(0.500,0.114592)(0.625,0.136021)(0.750,0.152418)(0.875,0.139939)(1.000,0.234379)
                };

                \addplot[
                    color=cyan,
                    mark=square
                ] coordinates {
                    (0.125,0.0198319)(0.250,0.0370639)(0.375,0.0415253)(0.500,0.0840702)(0.625,0.0623331)(0.750,0.0898241)(0.875,0.133761)(1.000,0.0869342)
                };
                \addplot[
                    color=red,
                    mark=halfcircle
                ] coordinates {
                    (0.125,0.0743185)(0.250,0.0810657)(0.375,0.113504)(0.500,0.145859)(0.625,0.256274)(0.750,0.266855)(0.875,0.259101)(1.000,0.274269)
                };

                \addplot[
                    color=red,
                    mark=square
                ] coordinates {

                    (0.125,0.02986)(0.250,0.0502663)(0.375,0.0717319)(0.500,0.0846663)(0.625,0.0966577)(0.750,0.123886)(0.875,0.139487)(1.000,0.132201)
                };
                \addplot[
                    color=MyGreen,
                    mark=halfcircle
                ] coordinates {
                    (0.125,0.0670488)(0.250,0.0926269)(0.375,0.0973621)(0.500,0.137059)(0.625,0.155913)(0.750,0.290065)(0.875,0.164799)(1.000,0.317625)
                };

                \addplot[
                    color=MyGreen,
                    mark=square
                ] coordinates {

                    (0.125,0.0325697)(0.250,0.0486132)(0.375,0.0750567)(0.500,0.0918979)(0.625,0.11031)(0.750,0.0755826)(0.875,0.168386)(1.000,0.174149)
                };
                \addplot[
                    color=orange,
                    mark=halfcircle
                ] coordinates {
                    (0.125,0.0313599)(0.250,0.044124)(0.375,0.0643389)(0.500,0.0684951)(0.625,0.0853552)(0.750,0.0532733)(0.875,0.064386)(1.000,0.0873334)
                };

                \addplot[
                    color=orange,
                    mark=square
                ] coordinates {

                    (0.125,0.0178225)(0.250,0.0373191)(0.375,0.0497523)(0.500,0.0684615)(0.625,0.0536034)(0.750,0.0618511)(0.875,0.129302)(1.000,0.12792)
                };
                \addplot[
                    color=black,
                    thick,
                    domain=0.1:1,
                    samples=200,
                ] {0.1*x^(0.5)} node[pos=0.5, anchor=north east] {$h^{\frac{1}{2}}$};
            \end{axis}
        \end{tikzpicture} \\
        \multicolumn{2}{c}{
            \begin{tikzpicture}
                \begin{axis}[
                    hide axis,
                    xmin=0, xmax=1,
                    ymin=0, ymax=1,
                    legend columns=3,
                    legend style={
                        at={(0.5,-0.2)},
                        anchor=north,
                        draw=none,
                        column sep=15pt,
                    }
                ]
                    \addlegendimage{mark=halfcircle}
                    \addlegendentry{VN}
                    \addlegendimage{mark=square}
                    \addlegendentry{II}
                    \addlegendimage{color=cyan}
                    \addlegendentry{ellipsoid}
                    \addlegendimage{color=red}
                    \addlegendentry{goursat}
                    \addlegendimage{color=MyGreen}
                    \addlegendentry{rcube}
                    \addlegendimage{color=orange}
                    \addlegendentry{sphere9}
